Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-09 supplement.tex
a few notes on specmatch results.

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

@@

>>>>

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
  This Work - BOSZ match & 4500 		& 4.5				& main-sequence star & high-resolution spectroscopy \\
  This Work - Specmatch 	&  4500 $\pm 110$ & 4.6 $\pm 0.1$ & main-sequence star & high-resolution spectroscopy \\ 
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

@@

\subsection{Specmatch}\label{sec:SpecMatch}

We also use the \texttt{specmatch} tool \citep{yee2017specMatch} to estimate the stellar parameters using the Subaru spectrum.
\texttt{specmatch} uses a library of Keck HIRES spectra to match the spectrum and derive stellar parameters.
Figure \ref{fig:specMatch} shows the chi-squared differences between the median Subaru spectrum and the models.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/spec_chi_min.pdf}
\caption{$\chi^2$ as a function of stellar parameters found by \texttt{specmatch}.}\label{fig:specMatch}
\end{centering}
\end{figure}
